The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-06 paper.tex
update

In the leptonic scenario, the gamma-rays originate from IC scattering of the ISRF by CRe.\
The CRe spectrum follows a power law distribution\
with a spectral index $p=2.4$ and ranges from\
$m_{\text{e}}c^2$ ($0.5$ MeV) to $1.1\times10^{6}m_{\text{e}}c^2$ ($550$ GeV).\

@@

where $\sigma_{T}$ is the Thomson cross section, $c$ speed of light,\
$n(\epsilon)$ the photon number density of ISRF per energy, $\gamma$ the Lorentz factor of CRe,\
$\mathbb{C}$ and $p$ are the normalization constant and spectral index of CRe power-law spectrum.
$\gamma_{\text{min}}(\epsilon)$ is the minimum required Lorentz factor of CRe such that CRe is energetic sufficient for\
producing scattered photon at the energy $\epsilon_{1}$ from an incident photon energy $\epsilon$.\
$\gamma_{\text{max}}$ is the maximum CRe Lorentz factor in the spectrum, i.e. $\gamma_{\text{max}}=10^{6}$.

@@

The gamma-ray emissivity\
is computed for each computational cell in our simulations\
using the Klein–Nishina IC cross-section \citep{Jones1968} based\
on the simulated CR number density and the ISRF model given by \citet{Porter2017}.

@@

  %The enhanced emission at the lower latitude would likely be due to
  %similar to the bottom right panel in Fig. 5 of YR17, which is dominated by\
  %the optical starlight. That's also why in your plot above,\
  %the high-latitude spectrum tends to be dimmer because of the decay of the ISRF intensity in optical.

>>>>

In the leptonic scenario, the gamma-rays originate from IC scattering of the interstellar radiation field by CRe.\
The CRe spectrum follows a power law distribution\
with a spectral index $p=2.4$ and ranges from\
$m_{\text{e}}c^2$ ($0.5$ MeV) to $1.1\times10^{6}m_{\text{e}}c^2$ ($550$ GeV).\

@@

where $\sigma_{T}$ is the Thomson cross section, $c$ speed of light,\
$n(\epsilon)$ the photon number density of interstellar radiation field per energy, $\gamma$ the Lorentz factor of CRe,\
$\mathbb{C}$ and $p$ are the normalization constant and spectral index of CRe power-law spectrum.
$\gamma_{\text{min}}(\epsilon)$ is the minimum required Lorentz factor of CRe such that CRe is energetic sufficient for\
producing scattered photon at the energy $\epsilon_{1}$ from an incident photon energy $\epsilon$.\
$\gamma_{\text{max}}$ is the maximum CRe Lorentz factor in the spectrum, i.e. $\gamma_{\text{max}}=10^{6}$.

@@

The gamma-ray emissivity\
is computed for each computational cell in our simulations\
using the Klein–Nishina IC cross-section \citep{Jones1968} based\
on the simulated CR number density and the interstellar radiation field model given by \citet{Porter2017}.

@@

  %The enhanced emission at the lower latitude would likely be due to
  %similar to the bottom right panel in Fig. 5 of YR17, which is dominated by\
  %the optical starlight. That's also why in your plot above,\
  %the high-latitude spectrum tends to be dimmer because of the decay of the interstellar radiation field intensity in optical.
